About the Beamer class in presentation making

### 2020-06-27 latex/slides/slides.tex
Rearrange the paper and slides folders
Update paper
Update slides

\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{utopia}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{siunitx}
\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}

@@

@@

\begin{frame}
  \frametitle{BERT architecture}
\end{frame}

@@

\begin{frame}
  \frametitle{Learning Rate Schedule}

  \begin{itemize}
    \item Warm-up steps: \num{10000};
    \item Learning rate: \num{1e-4};
  \end{itemize}

@@

  \includegraphics[width=\textwidth]{../latex-data/images/warmup_linear_schedule.png}
\end{frame}

@@

  \begin{itemize}
    \item Adam;
          \begin{itemize}
            \item Adam epsilon: \num{1e-4};
          \end{itemize}
    \item Batch size: \num{8};
    \item Training epochs: \num{32};
    \item Beam search hypothesis: \num{3};
  \end{itemize}
\end{frame}
%---------------------------------------------------------

@@

@@

  \begin{table}
    \centering
    \begin{tabularx}{\textwidth}{|X|X|c|}
      \hline
      \textbf{Email}                      & \textbf{Reply}                                                                              & \textbf{AI?} \\
      \hline
      Shall we have the meeting tomorrow? & meeting is postponed because the 3 : 00 p. m. meeting today. meeting is canceled for today. & \num{30}{\%} \\
      \hline
      hi                                  & Hi how are you?                                                                             & \num{10}{\%} \\
      \hline
      you look so handsome today          & why thank you, you do as well                                                               & \num{30}{\%} \\
      \hline
    \end{tabularx}
  \end{table}
\end{frame}
%---------------------------------------------------------

>>>>

\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{todonotes}
\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}

@@

  {\scriptsize
    yuck yuck
    \bigbreak
    -----Original Message-----
    \bigbreak
    har har
  }
  \bigbreak
  \bigbreak

  The subject is: \textbf{Wine tasting}.
\end{frame}

@@

\begin{frame}
  \frametitle{BERT architecture}

  \todo[inline]{Describe here the architecture that the professor showed in the class.}
\end{frame}

@@

\begin{frame}
  \frametitle{Learning rate schedule}

  \begin{itemize}
    \item Warm-up steps: \num{5000};
    \item Learning rate: \num{1e-4};
  \end{itemize}

@@

  \includegraphics[width=\textwidth]{../images/warmup_linear_schedule.pdf}
\end{frame}

@@

  \begin{itemize}
    \item Adam;
          \begin{itemize}
            \item Adam epsilon: \num{1e-4};
          \end{itemize}
    \item Batch size: \num{10};
    \item Training epochs: \num{10.5};
    \item Beam search hypothesis: \num{3};
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Loss function}

  \includegraphics[width=\textwidth]{../images/loss_function.pdf}
\end{frame}
%---------------------------------------------------------

@@

\begin{frame}
  \frametitle{BLEU score}

  \begin{itemize}
    \item <1-> 21 emails in the evaluation dataset;
    \item <2-> BLEU score = \num{0.0};
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{BLEU score}

  \begin{table}
    \begin{tabularx}{\textwidth}{|X|X|X|}
      \hline
      \textbf{Input}                                                  & \textbf{Target}                                          & \textbf{Generated}                                                                                                           \\
      \hline
      nevermind.  are you at work?                                    & yea                                                      & i'm all alone over here...                                                                                                   \\
      \hline
      what re your plans for tomorrow?                                & drop prentice's car off at shop; go to dome              & leaving early tomorrow. leaving early. leaving early. leaving early.                                                         \\
      \hline
      I just refaxed it.  For your information, my total hours is 49. & I noted your hours..I will look for the t/s Thanks Lisa! & Thanks Rick, and let's talk after the holidays about a new game plan... Best regards and happy thanksgiving. Jaime Williams. \\
      \hline
    \end{tabularx}
  \end{table}
\end{frame}

@@

  \begin{table}
    \scriptsize
    \begin{tabularx}{\textwidth}{|X|X|c|c|}
      \hline
      \textbf{Email}                                                                                                                                                                                        & \textbf{Reply}                                                                                                                                                                                                                     & \textbf{AI?} & \textbf{Correct?} \\
      \hline
      Let me know if this works.                                                                                                                                                                            & This works great. Will let you know. as soon as I get a chance, let me know                                                                                                                                                        & \num{0}{\%}  & yes               \\
      \hline
      Following are the terms under which I ran the Forward Obligation report and received this message: General SQL error. ORA-00907: missing right parenthesis. Terms: Let me know what you find. Thanks! & Kate, I ran the report with the exact same options and it came right up. Try it again, exactly as before. Usually if it works for one person and not the other it is a security issue. Let me know what happens. Thanks, Brettther & \num{0}{\%}  & yes               \\
      \hline
      Didn't you trade uranium at one time?                                                                                                                                                                 & Yeah, I know the buisness VERY well.                                                                                                                                                                                               & \num{0}{\%}  & no                \\
      \hline
      Are you free for drinks either Monday or Wednesday?                                                                                                                                                   & Yes                                                                                                                                                                                                                                & \num{0}{\%}  & no                \\
      \hline
      Mons, I would be available on the 25th, 26th or 27th. I cannot make it the week of the 18th. Thanks, Bill.                                                                                            & OK, so, let's see if we can get together later today. I have to leave at 16:00 for a few minutes, but I am sure that I will be out at that moment. Thank you Kim.                                                                  & \num{0}{\%}  & yes               \\
      \hline
    \end{tabularx}
  \end{table}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\section{Miscellaneous}

\begin{frame}
  \frametitle{Miscellaneous}

  \begin{itemize}
    \item \href{https://github.com/claudioscheer/seq2seq-bert}{https://github.com/claudioscheer/seq2seq-bert};
    \item \href{https://github.com/claudioscheer/seq2seq-bert/releases/tag/v0.0.8-alpha}{Final release (v0.0.8)};
  \end{itemize}
\end{frame}
%---------------------------------------------------------
